Demographic Species Distribution Models

### 2019-12-02 manuscript/ms.Rmd
drop confounded min temperature covariate

I fitted the model to a random subset of `r bbs_n_train` presence-absence records from the North American Breeding Bird Survey in 2015 [@sauerNorthAmericanBreeding2011]. I used six environmental covariates in $\mathbf{X}$: percentage cover of deciduous forest, coniferous forest, and mixed forest (to represent breeding habitat for this species), minimum temperature (to capture thermal limits on survival of the species), annual precipitation and mean temperature (as proxies for insect abundance and plant growth, food sources for this species). The forest cover layers were obtained from the maxlike R package [@royleLikelihoodAnalysisSpecies2012], and the climatic covariates were bioclim layers 6, 1, and 12 from the WorldClim 2.0 dataset [@fickWorldClimNew1km2017]. In general, ecological knowledge could be used to select separate covariates to use for each of the submodels. However, in the absence of a strong belief that any of these covariates would affect only one vital rate, all six covariates were used in both submodels. These covariate values were centred and scaled (before calculation of the priors on $\beta_F$ and $\beta_S$) to enable comparison of regreesion coefficients as effect sizes.

>>>>

I fitted the model to a random subset of `r bbs_n_train` presence-absence records from the North American Breeding Bird Survey in 2015 [@sauerNorthAmericanBreeding2011]. I used five environmental covariates in $\mathbf{X}$: percentage cover of deciduous forest, coniferous forest, and mixed forest (to represent breeding habitat for this species) mean temperature (to capture thermal limits on survival of the species), and annual precipitation (as a proxy for insect abundance and plant growth, food sources for this species). The forest cover layers were obtained from the maxlike R package [@royleLikelihoodAnalysisSpecies2012], and the climatic covariates were bioclim layers 1 and 12 from the WorldClim 2.0 dataset [@fickWorldClimNew1km2017]. In general, ecological knowledge could be used to select separate covariates to use for each of the submodels. However, in the absence of a strong belief that any of these covariates would affect only one vital rate, all six covariates were used in both submodels. These covariate values were centred and scaled (before calculation of the priors on $\beta_F$ and $\beta_S$) to enable comparison of regreesion coefficients as effect sizes.
